Run-Time Monitoring with Adjustable Overheads \\Using Dataflow-Guided Filtering

### 2014-12-18 policies.tex
Update to camera-ready formatting.
Various edits throughout paper.

% Slack
\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth]{figs/slack.pdf}
    \vspace{-0.3in}
    \caption{Slack and its effect on monitoring over time.}
    \label{fig:policies.slack}
    \vspace{-0.1in}
  \end{center}
\end{figure}

@@

Alternatively, we can specify a target overhead and estimate, at run-time, the
overheads of monitoring in order to decide whether dropping is needed.
The overhead budget is specified as a percentage of the main program's execution
cycles without monitoring. We define \emph{slack} as the number of cycles of
monitoring overhead that can be incurred while staying within the budget
target. Slack is essentially the difference between the actual overheads seen
and the budget specified. Slack is generated as the main program runs and consumed as monitoring overheads occur.  For
example, if no monitoring overheads occur during 1000 cycles of the main
program's execution and the designer sets a 20\% overhead target, then the
slack that is built up during this period is 200 cycles. If the main core is
then stalled for 50 cycles due to monitoring, then the remaining slack is 150
cycles. 
In addition to this accumulated slack, a small amount of initial slack
can be given in order for monitoring to be performed at the start of a program.
Figure~\ref{fig:policies.slack} shows an example of how slack can change over time.
In this slack-based policy, if the slack falls below zero (i.e., the overhead budget is exceeded), then
monitoring events should be dropped.

@@

\begin{figure}
  \begin{center}
  \subfloat[unrestricted dropping]{
    \includegraphics[width=\columnwidth, clip=true, trim=0 0.1in 0 0]{figs/all_drop.pdf}
    \label{fig:policies.all_drop}
  }
  \vspace{-0.1in}
  \\
  \subfloat[source-only dropping]{
    \includegraphics[width=\columnwidth, clip=true, trim=0 0.1in 0 0]{figs/source_drop.pdf}
    \label{fig:policies.source_drop}
  }
  \vspace{-0.1in}
%   \\
%   \subfloat[sub-flow dropping]{
%     \includegraphics[width=\columnwidth]{figs/min_drop.pdf}
%     \label{fig:policies.min_drop}
%   }
  \end{center}
  \vspace{-0.1in}
  \caption{Comparison of dropping policies using metadata dependence graphs.
  Square nodes represent events where check are performed. Blue (dark) nodes
  indicate which nodes can be dropped.}
  \label{fig:policies.policies}
\end{figure}

@@

An alternative dropping policy which eliminates this wasted work is to only make dropping decisions at
the root of these metadata flows. That is, we will decide to either monitor or
not monitor an entire metadata flow. We refer to this dropping decision policy
as \emph{source-only dropping} and we refer to the previous policy of 
dropping any event as \emph{unrestricted dropping}.

Figures~\ref{fig:policies.all_drop} and \ref{fig:policies.source_drop} show a
comparison of where dropping decisions are made for these two policies. Source
dropping will
result in no wasted work and thus better coverage. However, because of the coarser-grained decision, it
may be more difficult to closely match overheads. We expect source-only dropping 
to work well when there are a large number of independent metadata flows.
In addition, using a probabilistic dropping policy works poorly with
unrestricted dropping. Since each event in a dependent chain (e.g., events {\tt
A} through {\tt E}) needs to be monitored in order for the monitoring check to
be useful, randomly dropping any single event will cause the final check to be
invalid.

>>>>

% Slack
\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth]{figs/slack.pdf}
    \vspace{-0.2in}
    \caption{Slack and its effect on monitoring over time.}
    \label{fig:policies.slack}
    \vspace{-0.1in}
  \end{center}
\end{figure}

@@

Alternatively, we can specify a target overhead and estimate, at run-time, the
overheads of monitoring in order to decide whether dropping is needed.
The overhead budget is specified as a percentage of the main program's execution
cycles without monitoring. In order to estimate overheads at run-time, we define \emph{slack} as the number of cycles of
monitoring overhead that can be incurred while staying within the budget
target. Slack is essentially the difference between the actual overhead seen
and the budget specified. Slack is generated as the main program runs and consumed as monitoring overheads occur.  For
example, if no monitoring overheads occur during 1000 cycles of the main
program's execution and the designer sets a 20\% overhead target, then the
slack that is built up during this period is 200 cycles. If the main core is
then stalled for 50 cycles due to monitoring, then the remaining slack is 150
cycles. 
In addition to this accumulated slack, a small amount of initial slack
can be given in order for monitoring to be performed at the start of a program.
Figure~\ref{fig:policies.slack} shows an example of how slack can change over time.
In this slack-based policy, if the slack falls below zero (i.e., the overhead budget is exceeded), then
monitoring events should be dropped.

@@

\begin{figure}
  \begin{center}
  \subfloat[unrestricted dropping]{
    \includegraphics[width=\columnwidth, clip=true, trim=0 0.1in 0 0]{figs/all_drop.pdf}
    \label{fig:policies.all_drop}
  }
  \vspace{-0.1in}
  \\
  \subfloat[source-only dropping]{
    \includegraphics[width=\columnwidth, clip=true, trim=0 0.1in 0 0]{figs/source_drop.pdf}
    \label{fig:policies.source_drop}
  }
  \vspace{-0.1in}
%   \\
%   \subfloat[sub-flow dropping]{
%     \includegraphics[width=\columnwidth]{figs/min_drop.pdf}
%     \label{fig:policies.min_drop}
%   }
  \end{center}
  \caption{Comparison of dropping policies using metadata dependence graphs.
  Square nodes represent events where check are performed. Blue (dark) nodes
  indicate which nodes can be dropped.}
  \label{fig:policies.policies}
\end{figure}

@@

An alternative dropping policy which eliminates this wasted work is to only make dropping decisions at
the root or source of these metadata flows. That is, we will decide to either monitor or
not monitor an entire metadata flow. An example of these source nodes is the
monitoring done to initialize base and bounds information on {\tt malloc} for
an array bounds check. We refer to this dropping decision policy
as \emph{source-only dropping} and we refer to the previous policy of 
dropping any event as \emph{unrestricted dropping}.

Figures~\ref{fig:policies.all_drop} and \ref{fig:policies.source_drop} show a
comparison of where dropping decisions are made for these two policies. Source
dropping will
result in no wasted work and thus better coverage. However, because of the coarser-grained decision, it
may be more difficult to closely match overheads. We expect source-only dropping 
to work well when there are a large number of independent metadata flows.
In addition, using a probabilistic dropping policy works poorly with
unrestricted dropping. Since each event in a dependent chain (e.g., events {\tt
A} through {\tt E}) needs to be monitored in order for the monitoring check to
be useful, randomly dropping any event will cause the final check to be
invalid.
